---
title: "R Notebook"
output:
  html_notebook: 
    # fig_height: 5
    # fig_width: 7
    number_sections: yes
  html_document: default
---

# Post matlab stuff (MUST RUN FIRST)
## Here are all the brain regions and their systems
```{r, echo=F, message=F}
source("LoadLibs.R")
library("caret")
source("LoadProcessZ1New-dec18.R") #outputs knew.molten (df)
attach(knew.molten)

# Merge more details
freeze_details = read.csv("freeze_details.csv")
group_details = read.csv("group_details.csv", header=T, encoding = "UTF-8-BOM")
names(group_details)[1] = "GROUP"

knew.molten2 = merge(knew.molten, freeze_details, by="ID")
knew.molten2 = merge(knew.molten2, group_details, by="GROUP")

# Some NormOL values are NaN because it tried dividing by 0. 
# It should just be zero. 
knew.molten2 = knew.molten2 %>% mutate(value = ifelse(value=='NaN', 0, value))

# from now on I'm interested in densities and total
knew.molten3 = knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  filter(!CHANNEL=='OL')

# list the systems and their regions
list.brain.regions =  knew.molten3 %>% group_by(System) %>% select(System, SubROI_SubroiAGGR) %>% unique()
arrange(list.brain.regions, System)


```

# TOTAL brain, weighted average by ROI

## Tests for parametric assumptions
We used Bartlett's test to test the homoscedacity and Shapiro-Wilk test of normality. We did each test for each channel. Our total brain weighted means failed the normality test in all channels, so we did a box-cox transformation to make it more normal. Post-transformation, Arc, DAPI, and GFAP still failed normality at 95% confidence interval. 
```{r, eval=F}

# total brain weighted means
total.weighted = knew.molten3 %>%
  group_by(ID, GROUP, EXPT, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2))

# DESCRIPTIVES
total.weighted %>% ggplot() + aes(as.factor(ID), weighted, color=EXPT) + 
  geom_point() + facet_wrap(~CHANNEL, scales="free") + rx

# HISTOGRAMS
total.weighted %>% ggplot() + aes(weighted) + 
  geom_histogram() + facet_wrap(~CHANNEL, scales="free") + rx
  
# PLOT Q-Q
total.weighted %>%
  ggplot() + stat_qq(aes(sample=weighted, color=CHANNEL)) + 
  facet_wrap(~CHANNEL, scales="free") + theme_minimal()

# is my data skewed? check mean vs median
# probs want to find a metric for kurtosis though
total.weighted %>%
  group_by(CHANNEL) %>%
  summarize(mean = mean(weighted), median = median(weighted),
            "Rel. Difference (%)" = 100*abs(mean-median)/(mean+median),
            skewness = skewness(weighted))

# SHAPIRO-WILK test says that the means aren't normal
total.weighted %>%
  group_by(CHANNEL) %>%
  do(tidy(shapiro.test(.$weighted)))

# BARTLETT test says that the variances are the same
total.weighted %>%
  group_by(CHANNEL) %>%
  do(tidy(bartlett.test(.$weighted, .$GROUP)))

# TRIED DOING BOX-COX TRANSFORMATION
total.weighted.box = total.weighted %>% 
  group_by(CHANNEL) %>% 
  mutate(boxed = BoxCoxTrans(weighted) %>% predict(weighted))

# THEN TESTED SHAPIRO-WILK AGAIN
total.weighted.box %>%
  group_by(CHANNEL) %>%
  do(tidy(shapiro.test(.$boxed)))

# PLOT Q-Q AFTER BOX 
# PLOT Q-Q
total.weighted.box %>%
  ggplot() + stat_qq(aes(sample=box, color=CHANNEL)) + 
  facet_wrap(~CHANNEL, scales="free") + theme_minimal() +
  ggtitle("Box-Cox transformed Q-Q plots")


```

## Total cell density counts per channel
```{r}
knew.molten3 %>%
  filter(CHANNEL %in% c('ArcIHC', 'H2BGFP', 'NormOL', 'DAPI', 'GFAP')) %>%
  group_by(ID, GROUP, EXPT, VALENCE, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(CHANNEL, weighted) + 
  stat_summary(fun.y = "mean", geom="bar", position="dodge") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3), position=position_dodge(1)) + 
  ggtitle(paste(c("Whole brain, weighted, density"),"total","cells")) +
  theme_minimal() + rx +
  expand_limits(y=0)

knew.molten3 %>%
  filter(VALENCE == 'CONTEXT') %>%
  filter(System == 'SUBIC-HPC') %>%
  filter(CHANNEL %in% c('ArcIHC', 'H2BGFP', 'DAPI')) %>%
  group_by(ID, GROUP, EXPT, VALENCE, CHANNEL, SubROI_SubroiAGGR, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(CHANNEL, weighted) + 
  stat_summary(fun.y = "mean", geom="bar", position="dodge") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3), position=position_dodge(1)) + 
  facet_wrap(~SubROI_SubroiAGGR, ncol=12) +
  ggtitle(paste(c("Whole brain, weighted, density"),"total","cells")) +
  theme_minimal() + rx +
  expand_limits(y=0)

```


## Point-range graphs for each of the threshold levels
From the rest of the graphs, we ended up choosing the total cells. 
```{r}

knew.molten3 %>%
  filter(!(System==c('THALAMIC','MIDBRAIN','STRIATUM'))) %>%
  filter(CHANNEL %in% c('ArcIHC', 'H2BGFP', 'NormOL')) %>%
  group_by(ID, GROUP, EXPT, VALENCE, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(VALENCE, weighted, fill=EXPT) + 
  stat_summary(fun.y = "mean", geom="bar", position="dodge") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3), position=position_dodge(1)) + 
  facet_wrap(~CHANNEL, scales="free") +
  ggtitle(paste(c("Whole brain, weighted, density"),"total","cells")) +
  theme_minimal() + rx +
  expand_limits(y=0)

knew.molten3 %>%
  # filter((System!=c('THALAMIC','MIDBRAIN','STRIATUM'))) %>%
  filter(CHANNEL %in% c('ArcIHC', 'H2BGFP', 'NormOL')) %>%
  group_by(ID, GROUP, EXPT, VALENCE, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(EXPT, weighted, fill=VALENCE) + 
  stat_summary(fun.y = "mean", geom="bar", position="dodge") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3), position=position_dodge(1)) + 
  facet_wrap(~CHANNEL, scales="free") +
  ggtitle(paste(c("Whole brain, weighted, density"),"total","cells")) +
  theme_minimal() + rx +
  expand_limits(y=0)


knew.molten3 %>%
  # filter((System!=c('THALAMIC','MIDBRAIN','STRIATUM'))) %>%
  filter(CHANNEL %in% c('GFAP')) %>%
  group_by(ID, GROUP, EXPT, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(GROUP, weighted, fill=EXPT) + 
  stat_summary(fun.y = "mean", geom="bar", position="dodge") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3), position=position_dodge(1)) + 
  facet_wrap(~CHANNEL, scales="free") +
  ggtitle(paste(c("Whole brain, weighted, density"),"total","cells")) +
  theme_minimal() + rx +
  expand_limits(y=0)

```


## ANOVA on the Box-Cox transformed

```{r}
# aggregate into whole brains, then box cox transform
ts1 = knew.molten3 %>%
  ddply(., .(CHANNEL, GROUP, EXPT, VALENCE, CONTEXT, ID), summarize, wm = weighted.mean(value, Pop_roiAreaMM2)) %>%
  group_by(CHANNEL) %>%
  mutate(boxed = BoxCoxTrans(wm) %>% predict(wm))

# run the ANOVA on boxed data
ts2 = ts1 %>%
  group_by(CHANNEL) %>%
  do(tidy(aov(data=., boxed ~ EXPT * VALENCE * CONTEXT)))

# spit out significant values
ts2.sig = ts2 %>%
  filter(p.value < 0.05)
ts2.sig

# graph it
ts2 %>%
  filter(!(term=='Residuals')) %>%
  ggplot() + 
  aes(reorder(term, p.value), -log10(p.value), label=p.value, fill=CHANNEL) +
  geom_bar(stat="identity") +
  coord_flip() + theme_minimal() + rx +
  ggtitle(paste("Results, 3-way ANOVA (Box-Cox transform), line at p=0.05")) +
  ylab("p-value 10^-x") +
  xlab("System") +
  facet_wrap(~CHANNEL) +
  geom_hline(yintercept = 1.30103)

```

## ANOVA - post-hoc TukeyHSD
Oops this should probably be Dunn test if I do a KW test instead of ANOVA, bu I can't do a KW for 3-way
```{r}
hsd.ts1 = ts1 %>% 
  group_by(CHANNEL) %>%
  do(tidy(TukeyHSD(aov(data=., wm ~ EXPT * VALENCE * CONTEXT)))) %>%
  # select(term, comparison, adj.p.value) %>%
  filter(adj.p.value < 0.05) 

# eliminates the comparisons i don't want...
# parse out the comparison between '-' and ':' and compare
library(purrr)

# make a function that inputs hsd and spits out relevant comparisons only

compare.relevant = function(df) { #inputs hsd 
  sideA = unlist(map(strsplit(df$comparison, '-'), 1))
  sideB = unlist(map(strsplit(df$comparison, '-'), 2))
  
  sideA.elements = strsplit(sideA, ':')
  sideB.elements = strsplit(sideB, ':')
  
  keeps = sapply(
    mapply(match, sideA.elements, sideB.elements),
    function(x) length(x) - length(na.omit(x))
  )
  keeps = sapply(keeps, function(x) x==1)
  
  df.kept = df[keeps,]
  df.kept
}
# accept only relevant comparisons
hsd.ts1.relevant = compare.relevant(hsd.ts1)

# function to filter for only significant ANOVA
show.sig.from.anova = function(x,y) {
  sig.terms = paste(x$CHANNEL, x$term)
  rel.terms = paste(y$CHANNEL, y$term)
  
  y[rel.terms %in% sig.terms,]
}

# show only relevant AND significant ANOVA
show.sig.from.anova(ts2.sig, hsd.ts1.relevant)

```

## Kruskal-Wallis tests 
Because K-W tests can't do factorial designs you're probably going ot have to do the separate 1-way tests and then correct for n=14 multiple comparisons with Bonferroni (2^3 + 2^2 + 2^1)... Luckily the ANOVAs filter out which ones are most likely be important. There are no 3-ways. Let's just focus on the 2-ways and 1-ways.

```{r}

## ARCIHC EXPT:VALENCE
ts1 %>%
  filter(CHANNEL=='ArcIHC') %>%
  filter(EXPT=='OLD') %>%
  summarize(14*dunn.test(wm, VALENCE)$P)


ts1 %>%
  filter(CHANNEL=='ArcIHC') %>%
  filter(VALENCE == 'SHOCK') %>%
  summarize(14*dunn.test(wm, EXPT)$P)


## DAPI EXPT
ts1 %>%
  filter(CHANNEL=='DAPI') %>%
  # filter(EXPT=='OLD') %>%
  summarize(14*dunn.test(wm, EXPT)$P)

## GFAP EXPT, VALENCE
ts1 %>%
  filter(CHANNEL=='GFAP') %>%
  # filter(EXPT=='OLD') %>%
  summarize(14*dunn.test(wm, EXPT)$P)

ts1 %>%
  filter(CHANNEL=='GFAP') %>%
  # filter(EXPT=='OLD') %>%
  summarize(14*dunn.test(wm, VALENCE)$P)

## NORM OL EXPT:VALENCE
ts1 %>%
  filter(CHANNEL=='NormOL') %>%
  filter(EXPT=='YOUNG') %>%
  summarize(14*dunn.test(wm, VALENCE)$P)

```


## Linear regressions (total brain)
```{r, eval=F}
# shock lin reg
knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  filter(VALENCE == 'SHOCK') %>%
  group_by(ID, FREEZE,GROUP, EXPT, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(FREEZE, weighted) + 
  stat_summary(fun.y="mean", geom="point") +
  facet_wrap(EXPT~CHANNEL, scales="free", ncol=6) + geom_smooth(method="lm") +
  ggtitle("Total brain density vs freezing, total cells, shock animals only") +
  theme_minimal()

# all animals lin reg
knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  group_by(ID, FREEZE,GROUP, EXPT, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(FREEZE, weighted) + 
  stat_summary(fun.y="mean", geom="point") +
  facet_wrap(EXPT~CHANNEL, scales="free", ncol=6) + geom_smooth(method="lm") +
  ggtitle("Total brain density vs freezing, total cells, ALL animals") +
  theme_minimal()


 # GET THE STATS
tot.lr = knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  filter(VALENCE == 'SHOCK') %>%
  # filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
  
  group_by(CHANNEL, EXPT, GROUP, ID, FREEZE) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  
  group_by(CHANNEL, EXPT) %>%
  do(tidy(lm(data=., formula = weighted ~ FREEZE))) %>%
  filter(!term=="(Intercept)") %>%
  mutate(p.value = p.adjust(p.value, method="BH")) %>%
  mutate(sig = 
           case_when(
             p.value < 0.001 ~ "***",
             p.value < 0.01 ~ "**", 
             p.value < 0.05 ~ "*"
           ))


# positive or negative
tot.lr %>%
  filter(CHANNEL %in% c("H2BGFP","NormOL", "ArcIHC")) %>% # omit DAPI/OL/GFAP channels for clarity
  # dcast(., CHANNEL+EXPT ~ System, value.var="sig") %>%
  ggplot() + aes(EXPT, CHANNEL, fill=estimate/abs(estimate), label=round(estimate,0)) + geom_tile() +
  scale_fill_continuous(limits=c(-1,1), low="red", high="green", na.value="white") + 
  ggtitle("Slopes from linear regression (red is negative)") +
  theme_light()

# P VALUES
tot.lr %>%
  filter(CHANNEL %in% c("H2BGFP","NormOL", "ArcIHC")) %>% # omit DAPI/OL/GFAP channels for clarity
  # dcast(., CHANNEL+EXPT ~ System, value.var="sig") %>%
  ggplot() + aes(EXPT, CHANNEL, fill=p.value, label=sig) + geom_tile() +
  scale_fill_continuous(limits=c(0,0.05), low="dark red", high="white", na.value="white") + 
  ggtitle("Signifiance scores from linear regression (Holm corrected)") +
  theme_light() + geom_label(label.size=0, color="white")
```



# SYSTEMS analysis 

## Check normality
Fuck they fail normality again. 
```{r, eval=F}
# system brain weighted means
sys.weighted = knew.molten3 %>%
  group_by(ID, GROUP, EXPT, CHANNEL, variable, System) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2))

# SHAPIRO-WILK test says that the means aren't normal
sys.weighted %>%
  group_by(CHANNEL, System) %>%
  do(tidy(shapiro.test(.$weighted)))

# BARTLETT test says that the variances are the same
sys.weighted %>%
  group_by(CHANNEL, System) %>%
  do(tidy(bartlett.test(.$weighted, .$GROUP)))

sys.weighted.box = sys.weighted %>% 
  group_by(CHANNEL,System) %>% 
  mutate(boxed = BoxCoxTrans(weighted) %>% predict(weighted))

sys.weighted.box %>%
  group_by(CHANNEL, System) %>%
  do(tidy(shapiro.test(.$boxed)))

```


## ANOVA - Systems on Box-Cox
```{r}
# create weighted means for the system
ss1 = knew.molten3 %>%
  ddply(., .(CHANNEL, GROUP, EXPT, VALENCE, CONTEXT, ID, System), summarize,
        wm = weighted.mean(value, Pop_roiAreaMM2)) %>%
  mutate(boxed = BoxCoxTrans(wm) %>% predict(wm))

# do the ANOVA
ss2 = ss1 %>%
  group_by(CHANNEL, System) %>%
  do(tidy(aov(data=., boxed ~ EXPT * VALENCE * CONTEXT))) %>%
  mutate(p.value = p.adjust(p.value, method="BH"))
summary(ss2$p.value)
## fdr, mean p is 0.48
## fdr n=16, mean p is 0.72
## BH n=16, p = 0.72
## none, p = 0.36
## bonferroni, p = 0.75
## hommel, p=0.58

# how many significant systems?
ss2.sig = ss2 %>% filter(p.value < 0.05) 
summary(ss2.sig)

# make graphs
for (tm in unique(ss2$term)) {
    print(
      ss2 %>% 
        filter(term==tm) %>% 
        filter(!(term=='Residuals')) %>%
        ggplot() + aes(reorder(System, p.value), -log10(p.value), label=p.value, fill=System) + 
        geom_bar(stat="identity") +
        coord_flip() + theme_light() + rx +
        ggtitle(paste(tm, "3-way ANOVA on Box-Cox transformed")) +
        ylab("p-value 10^-x, Benjamini-Hochberg post-hoc") +
        xlab("System") +
        facet_wrap(~CHANNEL, ncol=3, scales="free") +
        geom_hline(yintercept = 1.30103)
    )
}

```

## Total systems percentage contribution
The goal here is to find out how much each system contributes to the overall whole brain counts. Still not sure if I did this right, because it should probably be done by size of area, not the total counts right? (REVISIT LATER)
```{r}
ss1.pct = ss1 %>% 
  filter(VALENCE=='CONTEXT') %>%
  group_by(CHANNEL) %>%
  mutate(T = sum(wm)) %>%
  group_by(System, add=T) %>% 
  mutate(per = 100*round(sum(wm)/T,2)) %>%
  summarize(rel.pct = mean(per)) 

ss1.pct %>%
  filter(CHANNEL %in% c('ArcIHC', 'H2BGFP', 'GFAP')) %>%
  ggplot() + aes(System, rel.pct, fill=System) + geom_bar(stat="identity", show.legend = F) +
  facet_wrap(~CHANNEL) + theme_minimal() + 
  ylab("Relative labeling (%)") +
  ggtitle("Labeling across brain systems are different by modality") + coord_flip()


```

## ANOVA - Post-hoc TukeyHSD
```{r}

hsd.ss1 = ss1 %>% 
  group_by(CHANNEL, System) %>%
  do(tidy(TukeyHSD(aov(data=., wm ~ EXPT * VALENCE * CONTEXT))))

dim(hsd.ss1)

# adjust p.value and filter for significant values
hsd.ss1.sig = hsd.ss1 %>% 
  mutate(adj.p.value2 = p.adjust(adj.p.value, method="BH")) %>%
  filter(adj.p.value2 < 0.05)

hsd.ss1.relevant = compare.relevant(hsd.ss1.sig)

# function to filter for only significant ANOVA
show.sig.from.anova.systems = function(x,y) {
  sig.terms = paste(x$CHANNEL, x$System, x$term)
  rel.terms = paste(y$CHANNEL, y$System, y$term)
  
  y[rel.terms %in% sig.terms,]
}

# show only relevant AND significant ANOVA
show.sig.from.anova.systems(ss2.sig, hsd.ss1.relevant)

remove_sme = function(df) {
  # find terms with ':', put in vector
  # parse out to create vector
  to.remove = a %>% filter(CHANNEL=='ArcIHC') %>% filter(System == 'MOTOR CTX') %>%
  filter(str_detect(term, ':')) %>% pull(term) %>% unique() %>% as.vector() %>%
  str_split(':') %>% unlist()
  
  # remove other terms that are in that vector
  df = df %>% filter(!(term %in% to.remove))
  df
}

a %>% group_by(CHANNEL, System) %>% remove_sme()
a

```


## Calculate weighted means for each system
```{r, fig.width = 7.5, fig.height=4}

# systems, weighted by ROI area
knew.molten2 %>%
  filter(CHANNEL %in% channel.list[c(2,3,4,6)]) %>%
  filter(UNITS == "density" & BRIGHTNESS == 'total') %>%
  # filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
  group_by(ID, System, GROUP, EXPT, VALENCE, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(VALENCE, weighted, color=EXPT) + 
  stat_summary(fun.y = "mean", geom="point") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.2)) + 
  facet_grid(CHANNEL~System, scales="free") +
  ggtitle("systems, weighted, density total cells, bad freezers NOT removed") + 
  theme_light() + rx


# systems, weighted by ROI area
# knew.molten2 %>%
#   filter(CHANNEL %in% channel.list[c(3,4,6)]) %>%
#   filter(UNITS == "density" & BRIGHTNESS == 'total') %>%
#   # filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
#   group_by(ID, System, GROUP, EXPT, CHANNEL, variable) %>%
#   summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
#   ggplot() + aes(GROUP, weighted, color=EXPT) + 
#   stat_summary(fun.y = "mean", geom="point") + 
#   stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.2)) + 
#   facet_wrap(CHANNEL~System, scales="free", ncol=15) + 
#   ggtitle("systems, weighted, density total cells, bad freezers NOT removed") + 
#   theme_light() + rx



```

## H2BGFP weighted means for each system
```{r, fig.height=2, fig.width=6}

# have to do GFP separately because AA/AB are the same...
knew.molten2 %>%
  filter(CHANNEL %in% channel.list[c(2)]) %>%
  filter(UNITS == "density" & BRIGHTNESS == 'total') %>%
  # filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
  group_by(ID, System, VALENCE, EXPT, CHANNEL, variable) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(VALENCE, weighted, color=EXPT, fill=EXPT) + 
  stat_summary(fun.y = "mean", geom="point") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.2)) + 
  facet_wrap(~System, scales="free", ncol=15) + 
  ggtitle("systems, weighted, density total cells, bad freezers NOT removed") + 
  theme_minimal() + rx + expand_limits(y=0) 

```

## Linear regressions 
- Do they correlate with how much fear they express? 
```{r, fig.width=9, fig.height=2}

# LINEAR REGRESSIONS SYSTEMS
for (ch in channel.list[c(2,3,5,6)]) {
  print(
    knew.molten2 %>%
      filter(UNITS == "density") %>%
      filter(BRIGHTNESS == 'total') %>%
      filter(VALENCE == 'SHOCK') %>%
      filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
      filter(CHANNEL == ch) %>%
      group_by(ID, System, GROUP, EXPT, CHANNEL, FREEZE, variable) %>%
      summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
      ggplot() + aes(FREEZE, weighted) + 
      stat_summary(fun.y="mean", geom="point") +
      facet_wrap(EXPT~System, scales="free", ncol=15) + geom_smooth(method="lm") +
      ggtitle(paste("Systems cell density vs freezing, shock animals only,", ch)) +
      theme_minimal() 
  )
}

 # GET THE STATS
sys.lr = knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  filter(VALENCE == 'SHOCK') %>%
  # filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
  group_by(CHANNEL, EXPT, GROUP, ID, FREEZE, System) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  
  group_by(CHANNEL, EXPT, System) %>%
  do(tidy(lm(data=., formula = weighted ~ FREEZE))) %>%
  filter(!term=="(Intercept)") %>%
  mutate(p.value = p.adjust(p.value, method="BH", n=16)) %>%
  mutate(sig = 
           case_when(
             p.value < 0.0005 ~ "***",
             p.value < 0.005 ~ "**", 
             p.value < 0.05 ~ "*"
           ))

# positive or negative
sys.lr %>%
  filter(CHANNEL %in% c("H2BGFP","NormOL", "ArcIHC")) %>% # omit DAPI/OL/GFAP channels for clarity
  # dcast(., CHANNEL+EXPT ~ System, value.var="sig") %>%
  ggplot() + aes(EXPT, System, fill=estimate/abs(estimate), label=round(estimate,0)) + geom_tile() + facet_wrap(~CHANNEL) + 
  scale_fill_continuous(limits=c(-1,1), low="red", high="green", na.value="white") + 
  ggtitle("Slopes from linear regression (red is negative)") +
  theme_light()

# P VALUES
sys.lr %>%
  filter(CHANNEL %in% c("H2BGFP","NormOL", "ArcIHC")) %>% # omit DAPI/OL/GFAP channels for clarity
  # dcast(., CHANNEL+EXPT ~ System, value.var="sig") %>%
  ggplot() + aes(EXPT, System, fill=p.value, label=sig) + geom_tile() + facet_wrap(~CHANNEL) + 
  scale_fill_continuous(limits=c(0,0.05), low="dark red", high="white", na.value="white") + 
  ggtitle("Signifiance scores from linear regression (FDR corrected)") +
  theme_light() + geom_label(label.size=0, color="white")
```


## Stats 2 (interactions)
```{r, eval=F}
sys.lr2 = knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  filter(VALENCE == 'SHOCK') %>%
  # filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
  group_by(CHANNEL, EXPT, GROUP, ID, FREEZE, System) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  group_by(CHANNEL) %>%
  do(tidy(lm(data=., weighted ~ FREEZE * EXPT))) %>%
  filter(!term=="Residuals") %>%
  # mutate(p.value = p.adjust(p.value, method="BH", n=16)) %>%
  mutate(sig = 
           case_when(
             p.value < 0.0005 ~ "***",
             p.value < 0.005 ~ "**", 
             p.value < 0.05 ~ "*"
           ))

sys.lr2 %>%
  filter(term=='FREEZE:EXPTYOUNG') %>%
  ggplot() + aes(reorder(CHANNEL, p.value), -log10(p.value), fill=CHANNEL) + 
  geom_bar(stat="identity") + coord_flip() + theme_minimal() +
  geom_hline(yintercept=2) +
  ggtitle("(Activity ~ Freeze):AGE") +
  xlab('channels')

knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  filter(VALENCE == 'SHOCK') %>%
  filter(!CHANNEL=='DAPI') %>%
  group_by(CHANNEL, EXPT, GROUP, ID, FREEZE, System) %>%
  summarize(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  ggplot() + aes(FREEZE, weighted, color=EXPT) +
  # geom_point() +
  geom_smooth(method="lm", fullrange=T, aes(group=EXPT)) +
  facet_wrap(~CHANNEL, scales="free") + theme_minimal() +
  ggtitle("Regressions of cell density vs. freezing") +
  ylab("Activated cell densities")

```


# REGIONS

## Density sorted per area
```{r}

for (ch in channel.list[c(2,3,4,5,6)]) {
  print(
    knew.molten3 %>%
      filter(CHANNEL == ch) %>%
      ggplot() + aes(reorder(SubROI_SubroiAGGR, value), value) + 
      stat_summary(fun.y = "mean", geom="point") + 
      stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3)) +
      rx + ggtitle(paste("Cell density measures per region - ", ch)) +
      facet_wrap(~EXPT)
  )
}

```


## Calculate the means for each ROI
Find the code from the other scripts you wrote. 

```{r, fig.width=12, fig.height=7}

for (ch in channel.list[c(3,4,5,6)]) {
  print(
    knew.molten3 %>%
      filter(CHANNEL == ch) %>%
      filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE=='SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
      ggplot() + aes(GROUP, value, color=EXPT) + 
      stat_summary(fun.y = "mean", geom="point") + 
      stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3)) + 
      facet_wrap(~SubROI_SubroiAGGR, scales="free", ncol=12) + 
      ggtitle(paste(c("Densities, shock animals only, removed poor performers, "),ch,", TOTAL cells")) +
      theme_light() + rx
  )
}

# and gfp
knew.molten3 %>%
  filter(CHANNEL == 'H2BGFP') %>%
  filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE=='SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
  ggplot() + aes(VALENCE, value, color=EXPT) + 
  stat_summary(fun.y = "mean", geom="point") + 
  stat_summary(fun.data = "mean_se", geom="errorbar", aes(width=0.3)) + 
  facet_wrap(~SubROI_SubroiAGGR, scales="free", ncol=12) + 
  ggtitle(paste(c("Densities, shock animals only, removed poor performers, "),"H2BGFP",", TOTAL cells")) +
  theme_light() + rx


```

## ANOVA - Subregions
```{r, fig.height=4, fig.width=8}
reg.stats = knew.molten3 %>%
  group_by(CHANNEL, SubROI_SubroiAGGR) %>%
  do(tidy(aov(data=., value ~ EXPT * VALENCE * CONTEXT))) %>%
  mutate(p.value = p.adjust(p.value, method="BH", n = 66)) %>%
  filter(p.value < 0.05)
```

### ANOVA - subregions with BH=66
```{r, fig.height=3, fig.width=6, eval=F}

for (tm in unique(reg.stats$term)) {
    print(
      reg.stats %>% 
        filter(term == tm & !(term=='Residuals')) %>%
        ggplot() + aes(reorder(SubROI_SubroiAGGR, p.value), -log10(p.value), label=p.value, fill=SubROI_SubroiAGGR) + 
        geom_bar(stat="identity") +
        theme_light() + rx +
        ggtitle(paste(tm, "(3-way ANOVA)")) +
        ylab("-log(p-value), Benjamini-Hochberg post-hoc for n=66 regions") +
        xlab("Subregions") +
        facet_wrap(~CHANNEL, scales = "free") +
        geom_hline(yintercept = 1.30103) +
        theme(text = element_text(size=10))
    )
}

```


### ANOVA - subreg for each signif. system

```{r}
significant.ss2 = ss2 %>%
  select(CHANNEL, System, term, p.value) %>%
  filter(p.value<0.05)

# for each channel
for (ch in channel.list) {
  for (sys in significant.ss2$System)) {
    knew.molten3
    
  }
}
# for each term
# find significant system
# get number of regions in that system
# then do the regions corrected for that number

```

## Heatmaps for ROI

```{r, fig.width=9, fig.height=4}

for (bright in c('low', 'mid', 'hi', 'total')[4]) {
  for (ch in channel.list) {
    print(
    knew.molten2 %>%
      filter(UNITS == "density") %>%
      filter(BRIGHTNESS == bright) %>%
      filter(CHANNEL == ch) %>%
      ddply(.(EXPT, SubROI_SubroiAGGR, CHANNEL), transform, z = scale(value)) %>%
      ggplot() + aes(GROUP, SubROI_SubroiAGGR, z=z, fill=z) +
      geom_tile() + scale_fill_gradient2(low='dark blue', mid='white', high='red') +
      facet_wrap(~EXPT, ncol=1) + rx + coord_flip() +
      ggtitle(paste("Scaled density across animals in age group,",bright, ch)) +
      theme_light() + rx
  )
  }
}
```



## Linear regressions for ROI
```{r, fig.width=12, fig.height=9, eval=F}

for (ch in channel.list[c(2,3,5,6)]) {
  print(
    knew.molten2 %>%
      filter(UNITS == "density") %>%
      filter(BRIGHTNESS == 'total') %>%
      filter(VALENCE == 'SHOCK') %>%
      filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
      filter(CHANNEL == ch) %>%
      ggplot() + aes(FREEZE, value) + 
      stat_summary(fun.y="mean", geom="point") +
      facet_wrap(EXPT~SubROI_SubroiAGGR, scales="free", ncol=16) + geom_smooth(method="lm") +
      ggtitle(paste("Subregion vs freezing, total cells, shock animals only,", ch)) +
      theme_minimal() 
  )
}

```

## Stats for linear regressions ROI
Looks like none of these subregions correlate with freezing... how is it possible that Systems do?
```{r, fig.height = 3, fig.width=5, eval=F}
 # GET THE STATS
roi.lr = knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') %>%
  filter(VALENCE == 'SHOCK') %>%
  # filter(!(EXPT =='YOUNG' & CONTEXT=='AA' & VALENCE == 'SHOCK' & FREEZE < 30)) %>% # removes young bad freezers
  
  group_by(CHANNEL, EXPT, GROUP, ID, SubROI_SubroiAGGR) %>%
  mutate(weighted = weighted.mean(value, Pop_roiAreaMM2)) %>%
  
  group_by(CHANNEL, EXPT, SubROI_SubroiAGGR) %>%
  do(tidy(lm(data=., formula = weighted ~ FREEZE))) %>%
  filter(!term=="(Intercept)") %>%
  mutate(p.value = p.adjust(p.value, method="BH", n=(66))) %>%
  mutate(sig = 
           case_when(
             p.value < 0.0005 ~ "***",
             p.value < 0.005 ~ "**", 
             p.value < 0.05 ~ "*"
           ))


# positive or negative
roi.lr %>%
  filter(CHANNEL %in% c("H2BGFP","NormOL", "ArcIHC")) %>% # omit DAPI/OL/GFAP channels for clarity
  # dcast(., CHANNEL+EXPT ~ System, value.var="sig") %>%
  ggplot() + aes(EXPT, SubROI_SubroiAGGR, fill=estimate/abs(estimate), label=round(estimate,0)) + geom_tile() + facet_wrap(~CHANNEL) + 
  scale_fill_continuous(limits=c(-1,1), low="red", high="green", na.value="white") + 
  ggtitle("Slopes from linear regression (red is negative)") +
  theme_light()

# P VALUES
roi.lr %>%
  filter(CHANNEL %in% c("H2BGFP","NormOL", "ArcIHC")) %>% # omit DAPI/OL/GFAP channels for clarity
  # dcast(., CHANNEL+EXPT ~ System, value.var="sig") %>%
  ggplot() + aes(EXPT, SubROI_SubroiAGGR, fill=p.value, label=sig) + geom_tile() + facet_wrap(~CHANNEL, ncol=1) + 
  scale_fill_continuous(limits=c(0,0.05), low="dark red", high="white", na.value="white") + 
  ggtitle("Signifiance scores from linear regression (Holm corrected)") +
  theme_light() + geom_label(label.size=0, color="white") + coord_flip() + rx


```


# MISC

```{r}

knew.molten3 %>%
  select(ID, EXPT, GROUP) %>%
  unique() %>%
  group_by(EXPT, GROUP) %>%
  summarize(number_animals = n())

```


