---
title: "R Notebook"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

# Group Legends
- SAB - shock AB
- SAA - shock AA
- CAB - context AB
- CAA - context AA

# Channel Legend
- Ch 1 = DAPI (stained)
- Ch 2 = GFP (experience 1)
- Ch 3 = GFAP (stained)
- Ch 4 = ARC (experience 2; stained)
- OL = overlap GFP/Arc
- OL.norm = overlap normalized to GFP/Arc

# EXPT legends
- AGE 10 = young mice
- AGE 11 = old mice

```{r}
# Load libraries
library(ggplot2)
library(reshape2)
library(dplyr)
library(plotrix)


# Load the data
rawkk = read.csv(file="All AGE 10 series counts-03232018/Wes_SUBROI_CLN_STACKED.csv", header=TRUE, sep=",")
rawkk$idBysubroi = as.factor(rawkk$idBysubroi)
colnames(rawkk)[2] = "GROUP"

# Merge animal details
animal_details = read.csv("animal_details.csv")
animal_details$Mouse.ID. = as.factor(animal_details$ID)
colnames(animal_details)[9] = "idBysubroi"
rawkk = merge(animal_details, rawkk, by = "idBysubroi")

attach(rawkk)


```


# Normalized densities per age group
```{r}

rawkk$OLmm2.norm = rawkk$OLmm2
rawkk$OLmm2.norm = rawkk$OLmm2/(rawkk$Ch2mm2 + rawkk$Ch4mm2 - rawkk$OLmm2)

# What is the mean count per brain, normalized to area?
channels.all = names(rawkk[13:18])


```

# Table of mean and SEM of densities per group
```{r}
# Get mean
young = filter(rawkk, EXPT=="AGE 10")
old = filter(rawkk, EXPT=="AGE 11")

age10.mean = aggregate(filter(rawkk[,13:18], EXPT=="AGE 10"), list(rawkk$GROUP[rawkk$EXPT=="AGE 10"]), mean)
age11.mean = aggregate(filter(rawkk[,13:18], EXPT=="AGE 11"), list(rawkk$GROUP[rawkk$EXPT=="AGE 11"]), mean)
head(age10.mean)
head(age11.mean)

# Get SEM
age10.se = aggregate(filter(rawkk[,13:18], EXPT=="AGE 10"), list(rawkk$GROUP[rawkk$EXPT=="AGE 10"]), std.error)
age11.se = aggregate(filter(rawkk[,13:18], EXPT=="AGE 11"), list(rawkk$GROUP[rawkk$EXPT=="AGE 11"]), std.error)
head(age10.se)
head(age11.se)

# # Check n
# age10.count = aggregate(filter(rawkk[,13:18], EXPT=="AGE 10"), list(rawkk$GROUP[rawkk$EXPT=="AGE 10"]), count)
# head(age10.count)
# 
# # Check variance
# age10.var = aggregate(filter(rawkk[,13:18], EXPT=="AGE 10"), list(rawkk$GROUP[rawkk$EXPT=="AGE 10"]), var)
# head(age10.var)


```



# Compare old/young for each group
- Question: What the fuck is going on with the differences here? Mean and SEM are in the table in previous section. 
```{r}
# How to use stat summmary to ggplot error bars
for (i in channels.all) {
  print (
    ggplot(rawkk) + 
      aes(x = GROUP, y = rawkk[i], fill=EXPT) +
      coord_flip() + 
      stat_summary(fun.y = mean, 
                   position="dodge",
                   geom="bar") +
      stat_summary(fun.data = mean_se, 
                   size=2,
                   position = "dodge",
                   geom="linerange") +
      ggtitle(i)
  )
}
```



# Look means at each SUBROI
```{r, fig.width=4,fig.height=7}
for (i in channels.all) {
  print (
    ggplot(rawkk) +
      aes(factor(SUBROI), rawkk[i], fill=EXPT) + 
      stat_summary(fun.y = mean, 
                   position="dodge",
                   geom="bar") +
      stat_summary(fun.data = mean_se, 
                   size=.5,
                   position="dodge",
                   geom="linerange") +
      ggtitle(i) + coord_flip() 
  )
}

```


# Now let's separate them by ROIs
- I'm not sure whether these error bars are correct... Are the SEMs factored out or not? How can these error bars be so small?
```{r}

# Make list of interesting ROIs
interesting.ROI = c("AcB", "CA1", "CA3", "CeA", "DG", "ENT","PAG", "PrL", "RSCla", "LA", "LAT")
ROI.acb = "AcB"

# Make pointrange graphs 
ggplot(rawkk[rawkk$SUBROI %in% ROI.acb,]) +
  aes(GROUP, OLmm2, fill=EXPT, shape=EXPT, color=EXPT) +
  stat_summary(fun.y = mean, 
               geom="point") +
  stat_summary(fun.data=mean_se, 
               geom="pointrange") +
  facet_wrap(~SUBROI)

# # check the SEM for the factored graph
# young.acb = filter(rawkk, EXPT=="AGE 10" & SUBROI=="AcB")
# young.acb.se = aggregate(young.acb[,13:18], list(young.acb$GROUP), std.error)
# head(young.acb.se)

# let's check if we can summarize the table by dplyr
rawkk[rawkk$SUBROI=="AcB",] %>% group_by(GROUP, EXPT) %>% summarize_if(is.numeric, mean)
rawkk[rawkk$SUBROI=="AcB",] %>% group_by(GROUP, EXPT) %>% summarize_if(is.numeric, std.error)


```




# For loop for each ROI
- Make a graph and the data table separately

```{r}

for (k in channels.all) {
  
  for (roi in interesting.ROI) {
    
    df = rawkk[rawkk$SUBROI %in% list(roi),]
    
    # Make pointrange graphs 
    print(
      ggplot(df) +
      aes(x=GROUP, y=df[,k], fill=EXPT, shape=EXPT, color=EXPT) +
      stat_summary(fun.y = mean, 
                   geom="point") +
      stat_summary(fun.data=mean_se, 
                   geom="pointrange") +
      facet_wrap(~SUBROI) + 
        labs(y = as.character(k))
    )
  #   
  #   # let's check if we can summarize the table by dplyr
  #   print(
  #     rawkk[rawkk$SUBROI==roi,] %>% 
  #       group_by(GROUP, EXPT) %>%
  #       summarize_if(is.numeric, mean)
  #   )
  #   print(
  #     rawkk[rawkk$SUBROI==roi,] %>% 
  #       group_by(GROUP, EXPT) %>% 
  #       summarize_if(is.numeric, std.error)
  #   )
  }
}




```


