---
title: "R Notebook"
output: html_notebook
---

# Inter-system correlations - TOTAL
Conditions in this set of graphs:
- 1. 'Total' cells only
- 2. Density measures
- 3. Correlations use "complete.obs"
- 4. Ordering by "hclust"
- 5. Removed bad freezers from young group

```{r}
source("LoadLibs.R")
library(corrplot)
library(ade4) # for mantel test! cor. mat dissimilarity
knew.molten3 = knew.molten2 %>%
  filter(UNITS == "density") %>%
  filter(BRIGHTNESS == 'total') 

library(corrplot)
library(Hmisc)
library(psych)
cluster.method = "alphabet"
use.method = "complete.obs"
corr.type="pearson"

```

# Define functions for getting correlation tests, making heatmaps
```{r}
# DEFINE FUNCTION FOR GETTING CORRELATION TEST
get_corrtest_sys = function(df) {
  data = df %>%
    # mutate(grain2 = paste(CHANNEL, System)) %>%
    ddply(.(CHANNEL, System), transform, z = scale(value)) %>%
    dcast(ID ~ System, value.var="z", fun.aggregate = mean) 
  
  # cor(data[,2:length(data)], data[,2:length(data)], use=use.method, method=corr.type)
    rcorr(as.matrix(data[,2:length(data)]), type=corr.type)
  
}


# DEFINE FUNCTION FOR MAKING HEATMAP
make_heatmap = function(test.results, title) {
  # inputs the results from 'get_corrtest'
  # matrix = test.results$r
  heatmap.2(test.results, symm=T, 
            col=rev(brewer.pal(11,"RdBu")), main=title, 
            trace="none", revC=T, margins=c(10,10),
            key=T, scale="none"
            )
}


# DEFINE FUNCTION FOR MAKING HEATMAP FOR NUMBER ANIMALS
make_heatmap2 = function(test.results, title) {
  # inputs the results from 'get_corrtest'
  # matrix = test.results$r
  # heatmap(test.results, symm=T, col=heat.colors, main=title)
  
  p = p.adjust(test.results$P, "fdr")
  
  corrplot(test.results$r, title=title, insig="blank", p.mat=test.results$P, sig.level=0.05,
           order=cluster.method, method="color", mar=c(0,0,1,0),
           diag=T, tl.pos = "l")
}
make_heatmap2(av1,"")




compare_matrix_r = function(x,y, namex, namey) {
  
  # MAKE COR MATS
  make_heatmap2(x, namex)
  make_heatmap2(y, namey)
  
  # PRINT T-TEST PAIRED
  x.vector = as.vector(x$r[lower.tri(x$r, diag=F)])
  y.vector = as.vector(y$r[lower.tri(y$r, diag=F)])
  print(t.test(fisherz(x.vector), 
               fisherz(y.vector), 
               paired=T))
  
  # PLOT DISTRIBUTION OF R VALUES
  df = data.frame(var = c(rep(namex, length(x.vector)), rep(namey, length(y.vector))), 
               values = c(x.vector, y.vector)) 
  print(
    df %>%
      ggplot() + aes(values, group=var, color=var) + geom_density() + 
      theme_minimal() + xlim(-1,1)
  )
  
  # PRINT DIFFERENCE MATRIX
  yx = y$r - x$r
  title = paste("Difference (", namey, " - ", namex, ")")
  corrplot(yx, title=title, order=cluster.method, method="color", 
           mar=c(0,0,1,0), diag=T, tl.pos = "l")


  # print(cor.test(x,y))
  
  print(
    df %>%
      ggplot() + aes(var, values) +
      stat_summary(fun.y = "mean", geom="bar") +
      stat_summary(fun.data = "mean_se", geom="errorbar") +
      theme_minimal())

}


```

# PCA

```{r}
get_data_matrix = function(df) {
  data = df %>%
    # mutate(grain2 = paste(CHANNEL, System)) %>%
    ddply(.(CHANNEL, System), transform, z = scale(value)) %>%
    dcast(ID ~ System, value.var="z", fun.aggregate = mean) 
  data
}

adm = arc %>% get_data_matrix()
rownames(adm) = adm$ID
adm = adm %>% select(2:16)
pr = prcomp(na.omit(adm), scale=T)
plot(pr$x[,1], pr$x[,2])
pr.var = pr$sdev^2
pr.var.pct = round(pr.var/(sum(pr.var)) * 100, 1)
barplot(pr.var.pct)
pr.data = data.frame(Sample=rownames(pr$x), X = pr$x[,1], Y = pr$x[,2])
ggplot(pr.data) + aes(X, Y, label=Sample) + geom_text()
pr.load = pr$rotation[,1]
sys.scores = abs(pr.load)
sys.scores.ranked = sort(sys.scores, decreasing=T)
names(sys.scores.ranked)
pr$rotation[names(sys.scores.ranked),1]

```


# ARCIHC
```{r}
# SUBSET FOR ARC ONLY
arc = knew.molten3 %>% filter(CHANNEL=='ArcIHC')
```


## Arc:: VALENCE maps
```{r}

# MAKE THE GRAPHS

for (val in levels(unique(knew.molten3$VALENCE))) {
  title = paste("all ArcIHC, ", val)
  a = arc %>%
    filter(VALENCE == val) %>%
    # filter(!(EXPT =='YOUNG' & GROUP=='SAA' & FREEZE < 30)) %>% # removes young bad freezers
    get_corrtest_sys() %>%
    make_heatmap2(., title)
}

```

### Arc::VALENCE stats = ns
```{r}

# Get Z dist of CONTEXT
av1 = arc %>%
  filter(VALENCE == 'CONTEXT') %>%
  get_corrtest_sys()

av2 = arc %>%
  filter(VALENCE == 'SHOCK') %>%
  get_corrtest_sys()



compare_matrix_r(av1, av2, "context", "shock")


```


## Arc::EXPT maps 
```{r, fig.width=5, fig.height=5}

# MAKE THE GRAPHS
for (age in (unique(knew.molten3$EXPT))) {
  title = paste("all ArcIHC, ", age)
  a = arc %>%
    filter(EXPT == age) %>%
    # filter(!(EXPT =='YOUNG' & GROUP=='SAA' & FREEZE < 30)) %>% # removes young bad freezers
    get_corrtest_sys() %>%
    make_heatmap2(., title)
}

```

### Arc::EXPT = ***
```{r}

# Get Z dist of CONTEXT
arc.age1 = arc %>%
  filter(EXPT == 'YOUNG') %>%
  get_corrtest_sys() 

arc.age2 = arc %>%
  filter(EXPT == 'OLD') %>%
  get_corrtest_sys() 


compare_matrix_r(arc.age1, arc.age2, "young", "old")



```



## Arc - EXPT:VALENCE Mantel test
```{r}

arc.ys = arc %>%
  filter(EXPT=='YOUNG') %>%
  filter(VALENCE=='SHOCK') %>%
  get_corrtest_sys()

arc.yc = arc %>%
  filter(EXPT=='YOUNG') %>%
  filter(VALENCE=='CONTEXT') %>%
  get_corrtest_sys()

arc.os = arc %>%
  filter(EXPT=='OLD') %>%
  filter(VALENCE=='SHOCK') %>%
  get_corrtest_sys()

arc.oc = arc %>%
  filter(EXPT=='OLD') %>%
  filter(VALENCE=='CONTEXT') %>%
  get_corrtest_sys()

```


### Arc Young CTX vs SHK = ***
```{r, fig.height=1, fig.width=2}

compare_matrix_r(arc.yc, arc.ys, "youngCTX", "youngSHK")
```

### Arc Old CTX vs SHK = ns
```{r, fig.height=1, fig.width=2}

compare_matrix_r(arc.oc, arc.os, "oldCTX", "oldSHK")
```





# H2BGFP
```{r}
# SUBSET FOR ARC ONLY
gfp = knew.molten3 %>% filter(CHANNEL=='H2BGFP')
```


## GFP:: VALENCE maps
```{r, fig.width=5, fig.height=5}

# MAKE THE GRAPHS
for (val in levels(unique(knew.molten3$VALENCE))) {
  title = paste("all H2BGFP, ", val, " withlow freezers removed")
  g = gfp %>%
    filter(VALENCE == val) %>%
    filter(!(EXPT =='YOUNG' & GROUP=='SAA' & FREEZE < 30)) %>% # removes young bad freezers
    get_corrtest_sys() %>%
    make_heatmap2(., title)
}

```

### GFP::VALENCE stats = ***
```{r}

# Get Z dist of CONTEXT
gv1 = gfp %>%
  filter(VALENCE == 'CONTEXT') %>%
  get_corrtest_sys()

gv2 = gfp %>%
  filter(VALENCE == 'SHOCK') %>%
  get_corrtest_sys()

compare_matrix_r(gv1, gv2, "context", "shock")


```


## GFP::EXPT maps 
```{r, fig.width=5, fig.height=5}

# MAKE THE GRAPHS
for (age in (unique(knew.molten3$EXPT))) {
  title = paste("all ArcIHC, ", age, " withlow freezers removed")
  g = gfp %>%
    filter(EXPT == age) %>%
    # filter(!(EXPT =='YOUNG' & GROUP=='SAA' & FREEZE < 30)) %>% # removes young bad freezers
    get_corrtest_sys() %>%
    make_heatmap(., title)
}

```

### GFP::EXPT = ns
```{r}

# Get Z dist of CONTEXT
gfp.age1 = gfp %>%
  filter(EXPT == 'YOUNG') %>%
  get_corrtest_sys() 

gfp.age2 = gfp %>%
  filter(EXPT == 'OLD') %>%
  get_corrtest_sys()

compare_matrix_r(gfp.age1, gfp.age2, "young", "old")
```



## GFP - EXPT:VALENCE Mantel test
```{r}

gfp.ys = gfp %>%
  filter(EXPT=='YOUNG') %>%
  filter(VALENCE=='SHOCK') %>%
  get_corrtest_sys() %>%
  as.dist()

gfp.yc = gfp %>%
  filter(EXPT=='YOUNG') %>%
  filter(VALENCE=='CONTEXT') %>%
  get_corrtest_sys() %>%
  as.dist()

gfp.os = gfp %>%
  filter(EXPT=='OLD') %>%
  filter(VALENCE=='SHOCK') %>%
  get_corrtest_sys() %>%
  as.dist()

gfp.oc = gfp %>%
  filter(EXPT=='OLD') %>%
  filter(VALENCE=='CONTEXT') %>%
  get_corrtest_sys() %>%
  as.dist()

```


### gfp Young CTX vs SHK = *
```{r}

mantel.rtest(gfp.ys, gfp.yc)
```

### gfp Old CTX vs SHK = **
```{r}

mantel.rtest(gfp.os, gfp.oc)
```



# NormOL
```{r}
# SUBSET FOR ARC ONLY
nol = knew.molten3 %>% filter(CHANNEL=='NormOL')
```


## NormOL:: VALENCE maps
```{r, fig.width=5, fig.height=5}

# MAKE THE GRAPHS
for (val in levels(unique(knew.molten3$VALENCE))) {
  title = paste("all NormOL, ", val, " withlow freezers removed")
  n = nol %>%
    filter(VALENCE == val) %>%
    filter(!(EXPT =='YOUNG' & GROUP=='SAA' & FREEZE < 30)) %>% # removes young bad freezers
    get_corrtest_sys() %>%
    make_heatmap(., title)
}

```

### NormOL::VALENCE stats = **
```{r}

# Get Z dist of CONTEXT
nv1 = nol %>%
  filter(VALENCE == 'CONTEXT') %>%
  get_corrtest_sys() 

nv2 = nol %>%
  filter(VALENCE == 'SHOCK') %>%
  get_corrtest_sys() 

compare_matrix_r(nv1, nv2, "context", "shock")

```


## NormOL::EXPT maps 
```{r, fig.width=5, fig.height=5}

# MAKE THE GRAPHS
for (age in (unique(knew.molten3$EXPT))) {
  title = paste("all NormOL, ", age, " withlow freezers removed")
  a = nol %>%
    filter(EXPT == age) %>%
    # filter(!(EXPT =='YOUNG' & GROUP=='SAA' & FREEZE < 30)) %>% # removes young bad freezers
    get_corrtest_sys() %>%
    make_heatmap(., title)
}

```

### NormOL::EXPT = ns
```{r}

# Get Z dist of CONTEXT
nol.age1 = nol %>%
  filter(EXPT == 'YOUNG') %>%
  get_corrtest_sys() %>%
  as.dist()

nol.age2 = nol %>%
  filter(EXPT == 'OLD') %>%
  get_corrtest_sys() %>%
  as.dist()

compare_matrix_r(nol.age1, nol.age2, "young", "old")

```

## NormOL - EXPT:VALENCE Mantel test
```{r}

nol.ys = nol %>%
  filter(EXPT=='YOUNG') %>%
  filter(VALENCE=='SHOCK') %>%
  get_corrtest_sys() %>%
  as.dist()

nol.yc = nol %>%
  filter(EXPT=='YOUNG') %>%
  filter(VALENCE=='CONTEXT') %>%
  get_corrtest_sys() %>%
  as.dist()

nol.os = nol %>%
  filter(EXPT=='OLD') %>%
  filter(VALENCE=='SHOCK') %>%
  get_corrtest_sys() %>%
  as.dist()

nol.oc = nol %>%
  filter(EXPT=='OLD') %>%
  filter(VALENCE=='CONTEXT') %>%
  get_corrtest_sys() %>%
  as.dist()

```


### NormOL Young CTX vs SHK = **
```{r}

mantel.rtest(nol.ys, nol.yc)
```

### NormOL Old CTX vs SHK = **
```{r}

mantel.rtest(nol.os, nol.oc)
```



```{r}

```

